Density dependence

### 2020-10-07 analysis/paper/appendix_density_dependence.Rmd
fixed up plots of 1d smooths.

```{r setup, include=FALSE}
knitr::opts_chunk$set(inclue = FALSE)
library(tidyverse)
library(here)
library(conflicted)
library(bbmle)
library(dlnm)
library(mgcv)

@@

-   Remove unnecessary dependencies

@@

```{r growth-plot, echo=FALSE, include=TRUE}
#TODO: show only s(log_shts), shift reference to intercept for model.
plot(g_growth, pages = 1)
```

@@

```{r growth-slice, echo=FALSE, include=TRUE}
pred_growth %>%
  filter(min_dist < 0.1) %>% 
  filter(lag == 1.75) %>% 
  ggplot(aes(x = x, y = exp(fitted), ymin = exp(fitted - 1.96*se.fit), ymax = exp(fitted + 1.96*se.fit))) +
  geom_line() + 
  geom_ribbon(alpha = 0.3) +
  geom_jitter(data = ha,
             aes(x = shts_1.5_2, y = shts_next),
             alpha = 0.1,
             inherit.aes = FALSE) +
  labs(title = "annulus 1.5–2m", 
       x = "conspecific density (shoots/m^2)",
       y = "#shoots (t+1)")
```

@@

```{r surv-plot, include=TRUE, echo=FALSE}
#TODO:
# - plot only size vs survival
# - back-transform shit
# - shift intercept
plot(g_surv, pages = 1)
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(inclue = FALSE)
library(tidyverse)
library(here)
library(conflicted)
library(bbmle)
library(dlnm)
library(mgcv)
# library(visibly)

@@

@@

```{r growth-plot, echo=FALSE, include=TRUE}
Q_new <- 
  g_growth$model %>% 
  pull(Q) %>%
  as_tibble() %>% 
  summarize(across(everything(), mean)) %>%
  as.matrix()
L_new <- L[1,, drop = FALSE]

newdata <- tibble(log_shts = seq(0, 2.565, length.out = 100), habitat = "1-ha", plot = "new", Q = Q_new, L = L_new)

fitted <- augment(g_growth, newdata = newdata, se_fit = TRUE, conf.level = 0.95)
ggplot(fitted, aes(x = exp(log_shts), y = exp(.fitted))) +
  geom_jitter(data = ha %>%
                filter(across(shts_0.5_1:shts_4.5_5, ~!is.na(.))),
              aes(x = shts, y = shts_next),
              alpha = 0.2) +
  geom_line(color = "blue") +
  geom_ribbon(aes(ymin = exp(.fitted - .se.fit*1.96), ymax = exp(.fitted + .se.fit*1.96)), alpha = 0.4) +
  labs(x = "#shoots (t)", y = "#shoots (t + 1)") +
  theme_bw()
```

@@

```{r growth-slice, echo=FALSE, include=TRUE}
pred_growth %>%
  filter(min_dist < 0.1) %>% 
  filter(lag == 1.75) %>% 
  ggplot(aes(x = x, y = exp(fitted), ymin = exp(fitted - 1.96*se.fit), ymax = exp(fitted + 1.96*se.fit))) +
  geom_jitter(data = ha %>%
                filter(across(shts_0.5_1:shts_4.5_5, ~!is.na(.))),
              aes(x = shts_1.5_2, y = shts_next),
              alpha = 0.2,
              inherit.aes = FALSE) +
  geom_line(color = "blue") + 
  geom_ribbon(alpha = 0.4) +

  labs(title = "annulus 1.5–2m", 
       x = "conspecific density (shoots/m^2)",
       y = "#shoots (t+1)") +
  theme_bw()
```

@@

```{r surv-plot, include=TRUE, echo=FALSE}
Q_new <- 
  g_surv$model %>% 
  pull(Q) %>%
  as_tibble() %>% 
  summarize(across(everything(), mean)) %>%
  as.matrix()
L_new <- L[1,, drop = FALSE]

newdata <- tibble(log_shts = seq(0, 2.565, length.out = 100), habitat = "1-ha", plot = "new", Q = Q_new, L = L_new)

fitted <- augment(g_surv, newdata = newdata, se_fit = TRUE)

#for rug
rugdat <- 
  ha %>%
  filter(across(shts_0.5_1:shts_4.5_5, ~!is.na(.))) %>% 
  mutate(survived = ifelse(surv == 1, shts, NA),
         died = ifelse(surv == 0, shts, NA))

ggplot(fitted, aes(x = exp(log_shts), y = plogis(.fitted))) +
  geom_line(color = "blue") +
  geom_ribbon(aes(ymin = plogis(.fitted - .se.fit*1.96), ymax = plogis(.fitted + .se.fit*1.96)), alpha = 0.4) +
  # geom_rug(data = rugdat,
  #          aes(x = survived),
  #          inherit.aes = FALSE,
  #          sides = "t",
  #          alpha = 0.2) +
  # geom_rug(data = rugdat,
  #          aes(x = died),
  #          inherit.aes = FALSE,
  #          sides = "b",
  #          alpha = 0.2) +
  stat_summary_bin(geom = "point",
                   fun = mean,
                   aes(y = surv),
                   bins = 1000,
                   data = ha %>%
                     filter(across(shts_0.5_1:shts_4.5_5, ~!is.na(.)))) +
  labs(x = "#shoots (t)", y = "survival probability") +
  scale_x_continuous(n.breaks = 7) +
  theme_bw()
```
